### 2025-05-10 tex/manuscript.tex
Autogenerate arXiv tarball

In this paper, we address this gap by providing the first comprehensive open database of Malaysian election results at the federal and state level -- we intend for this to be a living resource which provides the go-to empirical foundation for research and journalism on Malaysian elections. The database covers \textit{all} general elections since the pre-independence general election in 1955, and 115 by-elections held since 2008. In total, it records \TOTALBALLOTS\space ballots cast by \TOTALPARTIES\space individuals representing \TOTALPARTIES\space political parties in \TOTALCONTESTS\space unique electoral contests from 1955 to 2025. The dataset comprises two main components:
\begin{enumbul}
\item \textbf{Ballots}: The final results for each state legislative assembly constituency (DUN) and federal Parliament constituency (Parliament), with the number of votes received by each candidate.
\item \textbf{Summaries}: The electorate size, ballots issued, unreturned ballots, and votes rejected in each constituency. For each constituency, we also derive the margin of victory (majority), voter turnout rate, vote rejection rate, unreturned ballot rate, and majority as a share of valid votes.
\end{enumbul}

>>>>

In this paper, we address this gap by providing the first comprehensive open database of Malaysian election results at the federal and state level -- we intend for this to be a living resource which provides the go-to empirical foundation for research and journalism on Malaysian elections. The database covers \textit{all} general elections since the pre-independence general election in 1955, and 115 by-elections held since 2008. In total, it records \TOTALBALLOTS\space candidates representing \TOTALPARTIES\space political parties in \TOTALCONTESTS\space unique electoral contests from 1955 to 2025. The dataset comprises two main components:
\begin{enumbul}
\item \textbf{Ballots}: The final results for each state legislative assembly constituency (DUN) and federal Parliament constituency (Parliament), with the number of votes received by each candidate.
\item \textbf{Summaries}: The electorate size, ballots issued, unreturned ballots, and votes rejected in each constituency. For each constituency, we also derive the margin of victory (majority), voter turnout rate, vote rejection rate, unreturned ballot rate, and majority as a share of valid votes.
\end{enumbul}
